### 2013-07-03 Docs/visualization/visualization.tex

The main {\tt Header} is written by {\tt fabio\_ml\_multifab\_write\_d}

>>>>

The main {\tt Header} is written by {\tt fabio\_ml\_multifab\_write\_d} by
processor 0.  The information contained is the following:
\begin{quote}
NavierStokes-V1.1 \\
{\em number of variables} \\
{\em variable 1 name} \\
{\em variable 2 name} \\
$\vdots$ \\
{\em last variable name} \\
{\em number of dimensions} \\
{\em simulation time} \\
{\em number of levels} (0-based) \\
{\em physical domain minimum coordinate} (dm numbers) \\
{\em physical domain maximum coordinate} (dm numbers) \\
{\em jump in refinement between level 0 and 1} \\
$\vdots$ \\
{\em jump in refinement between level $n-2$ and $n-1$} \\
~\\

\end{quote}
